The ChEMBL database as Linked Open Data

### 2013-03-26 article.tex
reword statement about community alternative ontologies not yet available

Although many parts of the ChEMBL-RDF 13 dataset now use community based ontologies, some 
terms from the previous ad-hoc ontology are still used because no community alternative is yet available. 
These terms were created under the 
URI namespace \textit{http://rdf.farmbio.uu.se/chembl/onto/\#}, and are referenced here using the
prefix: \textit{chembl}.

>>>>

Although many parts of the ChEMBL-RDF 13 dataset now use community based ontologies, some 
terms from the previous ad-hoc ontology are still used when a community alternative is not yet available. 
These terms were created under the 
URI namespace \textit{http://rdf.farmbio.uu.se/chembl/onto/\#}, and are referenced here using the
prefix: \textit{chembl}.
